Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-02-01 CAV2018/paper.tex
add authors
formatting

Modern implementations of embedded control systems have proliferated with
the availability of low-cost devices that can perform highly non-trivial
control tasks, with significant impact in numerous application areas such as
life sciences, environmental control and robotics~\cite{astrom1997computer,
Franklin15}.  Correct synthesis of control software for such platforms is
non-trivial, even in cases with restricted dynamics.  We consider the case
of Linear Time Invariant (LTI) models, for which the synthesis of
controllers is well understood.  However, the use of digital control
architectures adds new challenges caused by artifacts specific to digital
control, such as the effects of finite-precision arithmetic (referred to
here as Finite Word Length or FWL effects), time discretization and
quantization errors introduced by A/D and D/A conversion.

@@

\paragraph{\underline{{\sc Refine Abstraction and optimize}}} refines the
model abstraction as well as optimizes the current candidate
solution.
%
First, the model abstraction must be refined in order to eliminate
the newly received counterexample. For this purpose,
we increase the time horizon $n$ for the
safety specification so that it captures the violating iteration
(for the given initial state) and adjust $\phi$ as 
$\phi := \phi \wedge \phi_\mathit{safety}^n$.
If the counterexample is provided by the {\sc continuous time} stage,
then we must select a smaller suitable sample time to be used
for the model discretization.
%% and modify the abstractions to meet the discretization 
%% ($\phi_{synth} = \phi_{synth} \wedge \phi_{sample}^{T_d'}$ and $\phi_{static} = \phi_{static} \wedge \phi_{sample}^{T_d'}$).
%% It will then feed back to the abstraction refinement loop to look for a suitable action for the updated model.
%\end{enumerate}

>>>>

Modern implementations of embedded control systems have proliferated with
the availability of low-cost devices that can perform highly non-trivial
control tasks, with significant impact in numerous application areas such as
life sciences, environmental control and robotics~\cite{astrom1997computer,
Franklin15}.  Correct synthesis of control software for such platforms is
non-trivial, even in cases with restricted dynamics.  We~consider the case
of Linear Time Invariant (LTI) models, for which the synthesis of
controllers is well understood.  However, the use of digital control
architectures adds new challenges caused by artifacts specific to digital
control, such as the effects of finite-precision arithmetic (referred to
here as Finite Word Length or FWL effects), time discretization and
quantization errors introduced by A/D and D/A conversion.

@@

\paragraph{\underline{{\sc Refine Abstraction and optimize}}} refines the
model abstraction as well as optimizes the current candidate
solution.
%
First, the model abstraction must be refined in order to eliminate
the newly received counterexample. For this purpose,
we increase the time horizon $n$ for the
safety specification so that it captures the violating iteration
(for the given initial state) and adjust $\phi$ as 
$\phi := \phi \wedge \phi_\mathit{safety}^n$.
If~the counterexample is provided by the {\sc continuous time} stage,
then we must select a smaller suitable sample time to be used
for the model discretization.
%% and modify the abstractions to meet the discretization 
%% ($\phi_{synth} = \phi_{synth} \wedge \phi_{sample}^{T_d'}$ and $\phi_{static} = \phi_{static} \wedge \phi_{sample}^{T_d'}$).
%% It will then feed back to the abstraction refinement loop to look for a suitable action for the updated model.
%\end{enumerate}
